clusters

### 2015-07-22 cluster.rmd
knn

#Biz.type
table(all7c$group.num, all7c$Biz.type)
#JD.Second table
table(all7c$group.num, all7c$JD.Second)
#combine JD.Second categories
all7c$JD.Second<- as.character(all7c$JD.Second)
#combine waste water and sewerage
all7c[all7c$JD.Second %in% 'sewerage',]$JD.Second<- 'waste water'
#combine re-use (water) and recycled water
all7c[all7c$JD.Second %in% 're-use (water)',]$JD.Second<- 'recycled water'
#combine water cycle management and water management and water strategy and flood studies
all7c[all7c$JD.Second %in% c('water cycle management', 'water strategy', 'flood studies'),]$JD.Second<-
        'water management'
#combine apartments and townhouses and community housing
all7c[all7c$JD.Second %in% c('townhouses','community housing','apartments'),]$JD.Second<- 'multi-dwelling'
#combine childcare and community
all7c[all7c$JD.Second %in% c('childcare', 'religious'),]$JD.Second<- 'community'
#combine commercial shop and dining
all7c[all7c$JD.Second %in% c('commercial shop','dining'),]$JD.Second<- 'dining/retail'
all7c$JD.Second<- as.factor(all7c$JD.Second)
all7c$JD.Second<- droplevels(all7c$JD.Second)

#Biz.type
table(all7c$group.num, all7c$pc.majpos)
```

@@

binary.build<- function(vars= vars.vec, df= all7d){
        options("contrasts")
        #create final df bin.knn
        bin.knn= rep(0, nrow(df))
        #loop through each variable in vars vector
        for(i in 1:2){
                temp = data.frame(df[, vars[i]])
                colnames(temp)<- c(vars[i])
                formula = paste('~',vars[i],'-1')
                a= model.matrix( as.formula(formula), temp)
                a= a[match(rownames(temp), rownames(a)),]
                bin.knn= cbind(bin.knn,a)
        }

        print(bin.knn)
}

binary.build(vars= vars.vec, df= all7d) %>% head
```

>>>>

#Biz.type
table(all7c$group.num, all7c$Biz.type)
#JD.Second table
table(all7c$group.num, all7c$JD.Second)
#combine JD.Second categories
all7c$JD.Second<- as.character(all7c$JD.Second)
#combine re-use (water) and recycled water
all7c[all7c$JD.Second %in% 're-use (water)',]$JD.Second<- 'recycled water'
#combine water cycle management and water management and water strategy and flood studies
all7c[all7c$JD.Second %in% c('water cycle management', 'water strategy'),]$JD.Second<-
        'water management'
#combine apartments and townhouses and community housing
all7c[all7c$JD.Second %in% c('townhouses','community housing','apartments'),]$JD.Second<- 'multi-dwelling'
#combine childcare and community
all7c[all7c$JD.Second %in% c('childcare', 'religious'),]$JD.Second<- 'community'
#combine commercial shop and dining
all7c[all7c$JD.Second %in% c('commercial shop','dining'),]$JD.Second<- 'dining/retail'
all7c$JD.Second<- as.factor(all7c$JD.Second)
all7c$JD.Second<- droplevels(all7c$JD.Second)

#Biz.type
table(all7c$group.num, all7c$Biz.type)
```

@@

binary.build<- function(vars= vars.vec, df= all7d){
        options("contrasts")
        #create final df bin.knn
        bin.knn= NULL
        #loop through each variable in vars vector
        for(i in 1:length(vars.vec)){
                temp = data.frame(df[, vars[i]])
                colnames(temp)<- c(vars[i])
                formula = paste('~',vars[i],'-1')
                a= model.matrix( as.formula(formula), temp)
                a= a[match(rownames(temp), rownames(a)),]
                bin.knn= cbind(bin.knn,a)
        }

        return(bin.knn)
}

knn.binary<- binary.build(vars= vars.vec, df= all7d)
knn.binary<- as.data.frame(knn.binary)

Have created binary matrix
Turn into dataframe and then perform jaccard distance nearest neighbour

# First turn new case into giant binary dataframe using function from above
new.case<- binary.build(vars= vars.vec, df= knn.binary %>% slice(2000))
